---
title: "Pin User & Group GUIDs for Audit Report"
output: html_document
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

## Pin User Information to RStudio Connect

List local users with the `GET /v1/users` endpoint. This endpoint uses offset pagination (using page numbers). Results are sorted by first name, then last name, then username, then email. When called with a prefix parameter (not used in this example), it searches for local users matching the prefix.

```{r}
library(httr)

# Request a page of up to 25 users.
resp <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"), "__api__/v1/users?page_size=25"),
  add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY")))
)
payload <- content(resp)

payload_list <- list()
# While the current page has results, add its contents to the list holder
# then advance to the next page.
while(length(payload$result) > 0) {

  payload_list[[length(payload_list) + 1]] <- payload$results

  # get the next page
  nextPage <- payload$current_page + 1
  resp <- GET(
    paste0(Sys.getenv("CONNECT_SERVER"), "__api__/v1/users?page_size=25&page_number=", nextPage),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY")))
  )
  payload <- content(resp)
}
```


```{r}
library(tidyr)

# Unnest the list of lists into a single column tibble of lists
users_list <- unnest_longer(tibble::tibble(dat = payload_list), dat) 

# Rectangle the tibble of lists into a tibble of usable column data
df_users <- unnest_wider(users_list, dat)
```


```{r}
library(pins)

# Pin the user data in df_users to RStudio Connect

# Pins will use CONNECT_API_KEY and CONNECT_SERVER by default,
# but we are being explicit here anyway.
pins::board_register_rsconnect(
  key = Sys.getenv("CONNECT_API_KEY"), 
  server = Sys.getenv("CONNECT_SERVER")
)

pins::pin(df_users, name = "user-info", description = "Results pulled from the /v1/users API", board = "rsconnect")
```

---

## Pin Groups Information to RStudio Connect 

List local groups with the `GET /v1/groups` endpoint. This endpoint uses offset pagination (using page numbers).

**Note: This endpoint is available only when groups are enabled in RStudio Connect and it will return an error otherwise.**

```{r}
library(httr)

# Request a page of up to 25 groups.
resp <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"), "__api__/v1/groups?page_size=25"),
  add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY")))
)
payload <- content(resp)

payload_list <- list()
# While the current page has results, add its contents to the list holder
# then advance to the next page.
while(length(payload$result) > 0) {

  payload_list[[length(payload_list) + 1]] <- payload$results

  # get the next page
  nextPage <- payload$current_page + 1
  resp <- GET(
    paste0(Sys.getenv("CONNECT_SERVER"), "__api__/v1/groups?page_size=25&page_number=", nextPage),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY")))
  )
  payload <- content(resp)
}
```


```{r}
library(tidyr)

# Unnest the list of lists into a single column tibble of lists
groups_list <- unnest_longer(tibble::tibble(dat = payload_list), dat) 

# Rectangle the tibble of lists into a tibble of usable column data
df_groups <- unnest_wider(groups_list, dat)
```


```{r}
library(pins)

# Pin the user data in df_groups to RStudio Connect

pins::pin(df_groups, name = "group-info", description = "Results pulled from the /v1/groups API", board = "rsconnect")
```