---
title: "Use connectapi to Generate Pins"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(connectapi) #will be on CRAN soon
library(rscview)
library(pins)
```

```{r envCheck, include=FALSE}
#Check that environment variables are set, exit knit if not.
check_envvars()
```

```{r}
client <- connect(
  host = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
)

pins::board_register_rsconnect(
  key = Sys.getenv("CONNECT_API_KEY"), 
  server = Sys.getenv("CONNECT_SERVER")
)
```

## All audit content will be given a tag. Specify that tag and hierarchy here:
```{r}
tag_name <- "Server Audit"
tag_parent <- "Projects and Presentations"
#create the tag -- will not give message if tag already exists.
create_tag_tree(client, tag_parent, tag_name)
```


---

## Pin User Information to RStudio Connect

List local users with the `connectapi` package.

```{r}
df_users <- get_users(client, limit = Inf)
```

```{r}
# Pin the user data in df_users to RStudio Connect

pins::pin(df_users, name = "user-info", description = "Results pulled from `connectapi::get_users()`", board = "rsconnect")
my_content <- content_item(client, pins::pin_info("katie/user-info", board = "rsconnect")$guid)
# tag it
set_content_tag_tree(my_content, tag_parent, tag_name)
# set_content_tags(pin_users, all_tags$`Projects and Presentations`$`Server Audit`)
```

---

## Pin Groups Information to RStudio Connect 

List local groups with the `connectapi` package.

**Note: This endpoint is available only when groups are enabled in RStudio Connect and it will return an error otherwise.**

```{r}
df_groups <- get_groups(client, limit = Inf)
```


```{r}
# Pin the user data in df_groups to RStudio Connect
pin_groups <- pins::pin(df_groups, name = "group-info", description = "Results pulled from `connectapi::get_groups()`", board = "rsconnect")

# tag it
set_content_tag_tree(pin_groups, tag_parent, tag_name)
```

---
## Pin Content List to RStudio Connect
List all content items visible to the requesting user.

Authenticated access from a user is required. If an "administrator" role is used, then all content items will be returned regardless of the visibility to the requesting user.

```{r}
library(httr)
library(tidyr)

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
content_list <- unnest_wider(tibble::tibble(dat = content(result)), dat)


# Use connectapi 
content_tbl <- get_content(client)


```

```{r}
library(pins)

# Pin the content data in content_list to RStudio Connect

pin_content <- pins::pin(content_list, name = "content-info", description = "Results pulled from the /v1/content API", board = "rsconnect")
# tag it
set_content_tag_tree(pin_content, tag_parent, tag_name)
```
