---
title: "Pin Group List for Audit Report"
output: html_document
---

```{r packages, include=FALSE}
library(rscview)
library(pins)
library(dplyr)

```


```{r check_envvars, include=FALSE}
check_envvars()
```


Authenticated access from a user is required. If an "administrator" role is used, then all content items will be returned regardless of the visibility to the requesting user.

## Pull Group Names and Group Members

```{r}
start_time <- Sys.time()
group_names_tbl <- connectapi::get_groups(src = create_connection(), limit = Inf) %>% dplyr::rename(group_name = name)
end_time <- Sys.time()
duration <- end_time - start_time
```

Info: `connectapi::get_groups()` took `r paste(round(duration[[1]], 2),  units(duration))` to run.


```{r}
start_time <- Sys.time()
group_members_tbl <- get_groups_tbl()

end_time <- Sys.time()
duration <- end_time - start_time
```

Info: `get_groups_tbl` took `r paste(round(duration[[1]], 2),  units(duration))` to run.

## Pin Group List to RStudio Connect
```{r pin_it}
create_pin(group_names_tbl, description = "Results pulled via `connectapi` for audit reports")
create_pin(group_members_tbl, description = "Results pulled via `connectapi` for audit reports")

```

```{r}
# TO DO: add a create_tag to collect all the pins and dashboards

# TO DO: add in a set_schedule command
```

