---
title: "Pin Content List for Audit Report"
output: html_document
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

List all content items visible to the requesting user.

Authenticated access from a user is required. If an "administrator" role is used, then all content items will be returned regardless of the visibility to the requesting user.

## Pin Content List to RStudio Connect

```{r}
library(httr)
library(tidyr)

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
content_list <- unnest_wider(tibble::tibble(dat = content(result)), dat) 
```

```{r}
library(pins)

# Pin the content data in content_list to RStudio Connect

# Pins will use CONNECT_API_KEY and CONNECT_SERVER by default,
# but we are being explicit here anyway.
pins::board_register_rsconnect(
  key = Sys.getenv("CONNECT_API_KEY"), 
  server = Sys.getenv("CONNECT_SERVER")
)

pins::pin(content_list, name = "content-info", description = "Results pulled from the /v1/content API", board = "rsconnect")
```