---
title: "Basic Content Audit w/ Email Update"
output: 
  html_document:
    theme: lumen
rmd_output_metadata:
  rsc_output_files:
    - "rsc-basic-audit.csv"
editor_options: 
  chunk_output_type: console
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

```{r package-load, include=FALSE}
library(httr)
library(xml2)
library(dplyr)
library(tidyr)
library(pins)
library(reactable)
library(blastula)
```

## List all content items on the RStudio Connect server and send a custom email update

To pull a complete list of the content items on your Connect server, you must use an API key generated from an Admin account. Publisher account API keys will only return content items which the publisher user has been given access to view or edit.

Requirements:

- [Administrator API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"}
- RStudio Connect server URL

```{r content-list, include=FALSE}

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
df_full <- unnest_wider(tibble::tibble(dat = content(result)), dat) 

df_full
```

### Download the full report contents

```{r include=FALSE}
# Write the full content list reponse out to a CSV file for download
write.csv(df_full, "rsc-basic-audit.csv", row.names=FALSE)
```

- Report: [rsc-basic-audit.csv](rsc-basic-audit.csv)

---

## Explore the content list report

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Filter the full response to select specific fields for viewing
df_view <- df_full %>%
  select(name, title, owner_guid, dashboard_url, app_mode, access_type, r_version, py_version, created_time, last_deployed_time)

# cross with the user pin to map owner_guid to username
df_users <- pin_get("katie/user-info", board = "rsconnect")
user_lookup <- df_users %>% select(username, guid)

df_view <- df_view %>% left_join(user_lookup, by = c("owner_guid" = "guid")) %>%
  relocate(username, .after = title) %>% relocate(owner_guid, .after = last_deployed_time)

# Use reactable to create a nicely formatted table
reactable(df_view, searchable = TRUE, highlight = TRUE, resizable = TRUE,
  filterable = TRUE, columns = list(
  name = colDef(name = "Name"),
  title = colDef(name = "Title"),
  username = colDef(name = "Username"),
  dashboard_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    }),
  app_mode = colDef(name = "Type"),
  access_type = colDef(name = "Access Level"),
  r_version = colDef(name = "R Version"),
  py_version = colDef(name = "Python Version"),
  created_time = colDef(name = "Created", format = colFormat(datetime = TRUE)),
  last_deployed_time = colDef(name = "Last Deployed", format = colFormat(datetime = TRUE))
))
```


```{r connect_email, include=FALSE}
# Attach a custom email
render_connect_email(input = "content-audit-email.Rmd") %>%
  attach_connect_email(
    subject = "RStudio Connect Content Audit"
  )
```
