---
title: "CHANGE ME RStudio Connect Usage - Last `r as.numeric(Sys.getenv('DAYSBACK', 30))` Days"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    css: custom.css
    theme:
      version: 4
      fg: "#4C8187"
      bg: "#fff"
editor_options: 
  chunk_output_type: console
---

## Katie's notes
So far as I can tell, audit logs dont contain interesting information about content access. Presumably because audit logs are about server and user actions. Not in accessing content.


```{r}
library(connectapi)
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(rscview)
library(pins)
library(sunburstR)
library(d3r)
```

```{r check_envvars, include=FALSE}
check_envvars()
```

```{r get_users_and_logs, include=FALSE}
conn <- create_connection()


#get a table with content name and deployment info
# content <- get_content(conn, limit = Inf)
# content <- readr::read_rds(here::here("inst", "usage-report", "content_2021-06-14.rds"))
content_list <-pin_get("katie/content_list", board = "rsconnect")

content_info_tbl <- content_list %>% 
  dplyr::select(guid, name, title, owner_username, url, app_mode, content_category, access_type, py_version, r_version)

#Notes for future self - from `https://github.com/rstudio/connectapi/blob/002f0a6a0a6d3cf2eadc57f3daf173dd13ca65ff/R/ptype.R#L56`
#(1=shiny, 2=shiny Rmd, 3=source Rmd, 4=static, 5=api, 6=tensorflow, 7=python, 8=flask, 9=dash, 10=streamlit)
type_ref <- tibble(app_mode = 1:10, 
                   content_type = c("Shiny", 
                                   "Shiny RMD",
                                   "Source RMD", 
                                   "Static", 
                                   "API", 
                                   "Tensorflow", 
                                   "Python", 
                                   "Flask", 
                                   "Dash", 
                                   "Streamlit"))

content_info_tbl <- content_info_tbl %>% left_join(type_ref, by = "app_mode")

user_info_tbl <- get_users_tbl(conn)
```


```{r setup, include=FALSE}

# days_back <- 90 #days
months_back <- 3 #months
# ^^--- this needs to be added to a global variable. this goes into the ETL that pins the shiny / nonshiny usage pins. 
## TODO create a test to see how long each API calls and advise if a pin should be used or if running the call live is okay.

#I think we dont need this --v
# default_content_title <- "Unknown (Deleted Content?)"

report_from <- lubridate::today() - lubridate::dmonths(months_back)

# shiny_raw <- get_usage_shiny(
#   conn,
#   from = report_from,
#   limit = Inf
# ) %>%
#   mutate(
#     started = lubridate::ymd_hms(started),
#     ended = lubridate::ymd_hms(ended),
#     session_duration = ended - started
#     ) %>%
#   filter(session_duration > lubridate::dseconds(5))

# shiny_raw <- read_rds(here::here("inst", "usage-report", "shiny_2021-06-14.rds"))
shiny_raw <- pin_get("katie/shiny_raw_usage", board = "rsconnect")
shiny <- shiny_raw %>% select(-ended)

# start_time <- Sys.time()
# other_raw <- get_usage_static(
#   conn,
#   from = report_from,
#   limit = Inf
# )
# end_time <- Sys.time()
# duration_get_other <- end_time - start_time

other_raw <- pin_get("katie/nonshiny_raw_usage", board = "rsconnect")
# other_raw <- read_rds(here::here("inst", "usage-report", "static_2021-06-14.rds"))

other <- other_raw %>% select(-variant_key, -rendering_id, -bundle_id) %>% 
  rename("started" = time)

## TO DO - ask - does flask and other interactive content in the "other" category no session duration?

# all_users <- get_users(conn, page_size = 500)


access_data <- bind_rows(shiny, other) %>% 
  mutate(session_duration_mins = as.numeric(session_duration)/60) %>% 
  select(-session_duration)
# readr::write_rds(data, file = here::here("inst","usage-report", "data.rds"))


access_details <- access_data %>% left_join(content_info_tbl, by = c(content_guid = "guid")) %>% 
  left_join(select(user_info_tbl, username, guid), by = c(user_guid = "guid"))

# Note - curious thing to look into - what is the content that doesnt seem to exist with long durations? was this since deleted and thats why it has no info?  content guid example a3a16278-fca0-4592-a547-e7087395571f

# WHAT IS NA for acl? <- it's the same as content_type == NA.  but what is it?  
# how is NA username accessing content that is acl, logged_in?
authenticated_access <- access_details %>% filter(access_type != "all") 
## ^ check this.

```

This content summary may contain privileged information. The report is generated
using the [RStudio Connect Server API](http://docs.rstudio.com/connect/api) and
the source code is [available online](https://github.com/sol-eng/connect-usage)
if you'd like to customize your analysis. Data is limited to the last `r
days_back` days.

The report uses the environment variables `CONNECT_SERVER` and `CONNECT_API_KEY`
to collect the data. To limit the results to a single publisher, use a publisher
API key.

Row 
-----------------------------------------------------------------------
What content is most popular?
```{r}

get_top_n_visited <- function(access_details, monthsback = months_back, n = Inf){
  access_details %>%
  filter(started > today() - dmonths(months_back)) %>% 
  mutate(month = round_date(started, "month")) %>% 
  group_by(month, content_guid, user_guid, name, title, owner_username, access_type, content_type, username) %>% 
  summarise(visits = n(), .groups = "drop") %>% 
  arrange(desc(visits)) %>% 
    head(n)
}

```


# R vs Python content
```{r}
#the vision: sunburst plot of R vs Python and version of each used. <- wonder if we should color special the reticulated items :)

content_tbl_lang <- content_info_tbl %>% 
  select(guid, name, title, r_version, py_version, content_category) %>% 
  # select(-guid, -content_category, -name) %>% 
  filter(!(is.na(r_version) & is.na(py_version))) %>% 
  rename("R" = r_version, "Python" = py_version) %>% 
  pivot_longer(cols = c(R, Python), names_to = "language", values_to = "version") %>% 
  filter(!is.na(version)) %>% 
  group_by(language, version) %>% summarise(count = n()) %>% 
  mutate(path = paste(language, version, sep = "-")) %>% ungroup() %>% 
  select(path, count)

my_colors <- list(range = c(calls_account_color$acct_color, opps_color$opp_color),
                  domain = c(calls_account_color$account_name_days, opps_color$opp_name_days))


sund2b(content_tbl_lang, 
       valueField = "count",
       # colors = my_colors, 
       rootLabel = "All Content", 
       width = "100%",
       # breadcrumbs = sund2bBreadcrumb(enabled = FALSE),
       showLabels = TRUE
       )

sunburst(content_tbl_lang)

```



```{r}

summary_access <- get_top_n_visited(access_details, months_back)

## NEED HELP with this plot -- cant get it in pareto sort and want to filter results

visits_by_month_tbl <-
  summary_access %>% 
  dplyr::select(month, visits, content_type) %>%
  dplyr::group_by(month, content_type) %>%
  dplyr::summarize(n = n(), .groups = "keep") %>%
  dplyr::arrange(desc(month), desc(n)) %>%
  dplyr::
  

ggplot(
  data = visits_by_month_tbl,
  aes(x = month, y = visits)
  ) + 
  geom_bar(stat = "identity") +  
     labs(
       x = NULL,
       y = "Number of Visits"
     ) + 
  facet_wrap(~ content_type, scales = "free") +
  scale_x_datetime(date_labels = "%m %Y")


get_top_n_visitors <- function(access_details, monthsback = months_back, n = Inf){
  access_details %>%
    filter(!is.na(user_guid)) %>% 
  filter(started > today() - dmonths(months_back)) %>% 
  mutate(month = round_date(started, "month")) %>% 
  group_by(month, user_guid, name, title, owner_username, access_type, content_type, username) %>% 
  summarise(visits = n()) %>% arrange(desc(visits)) %>% head(n)
}


  

# Create top N chart of most frequently visited pieces of content. 
# Also create filter by publisher
# and summary of number of things published by usernae



```


```{r}


access_details %>% 
  filter(username == "katie") %>% group_by(content_guid, title, name, owner_username, content_type) %>% 
  summarise(visits = n()) %>% arrange(desc(visits)) 
#what content has a user visited?
get_user_access_activity <- function(access_details, user_guid) {
  access_details %>% filter(user_guid == !!user_guid)
}

get_user_access_activity(access_details, my_guid) %>% 
  get_top_n_visited()

#what users visit a piece of content most?
get_content_access_activity <- function(access_details, content_guid){
  access_details %>% filter(content_guid == !!content_guid)
}


get_content_access_activity(authenticated_access, (get_top_n_visited(authenticated_access)$content_guid)[3]) %>% 
  get_top_n_visitors()

#what apps have the largest number of users
authenticated_access %>% get_top_n_visitors()

```
 
