---
title: "CHANGE ME RStudio Connect Usage - Last `r as.numeric(Sys.getenv('DAYSBACK', 30))` Days"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    css: custom.css
    theme:
      version: 4
      fg: "#4C8187"
      bg: "#fff"
editor_options: 
  chunk_output_type: console
---

## Katie's notes
So far as I can tell, audit logs dont contain interesting information about content access. Presumably because audit logs are about server and user actions. Not in accessing content.


```{r}
library(connectapi)
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(rscview)
```

```{r check_envvars, include=FALSE}
check_envvars()
```

```{r get_users_and_logs, include=FALSE}
conn <- create_connection()


#get a table with content name and deployment info
# content <- get_content(conn, limit = Inf)
# content <- readr::read_rds(here::here("inst", "usage-report", "content_2021-06-14.rds"))
content_list <-pin_get("katie/content_list", board = "rsconnect")

content_info <- content %>% 
  select(guid, name, title, owner_username, url, app_mode, content_category, access_type)

#Notes for future self - from `https://github.com/rstudio/connectapi/blob/002f0a6a0a6d3cf2eadc57f3daf173dd13ca65ff/R/ptype.R#L56`
#(1=shiny, 2=shiny Rmd, 3=source Rmd, 4=static, 5=api, 6=tensorflow, 7=python, 8=flask, 9=dash, 10=streamlit)
type_ref <- tibble(app_mode = 1:10, 
                   content_type = c("Shiny", 
                                   "Shiny RMD",
                                   "Source RMD", 
                                   "Static", 
                                   "API", 
                                   "Tensorflow", 
                                   "Python", 
                                   "Flask", 
                                   "Dash", 
                                   "Streamlit"))

content_info <- content_info %>% left_join(type_ref, by = "app_mode")
```


```{r setup, include=FALSE}

# days_back <- 90 #days
months_back <- 3 #months
# ^^--- this needs to be added to a global variable. this goes into the ETL that pins the shiny / nonshiny usage pins. 
## TODO create a test to see how long each API calls and advise if a pin should be used or if running the call live is okay.

#I think we dont need this --v
# default_content_title <- "Unknown (Deleted Content?)"

report_from <- lubridate::today() - lubridate::dmonths(months_back)

# shiny_raw <- get_usage_shiny(
#   conn,
#   from = report_from,
#   limit = Inf
# ) %>%
#   mutate(
#     started = lubridate::ymd_hms(started),
#     ended = lubridate::ymd_hms(ended),
#     session_duration = ended - started
#     ) %>%
#   filter(session_duration > lubridate::dseconds(5))

# shiny_raw <- read_rds(here::here("inst", "usage-report", "shiny_2021-06-14.rds"))
shiny_raw <- pin_get("katie/shiny_raw_usage", board = "rsconnect")
shiny <- shiny_raw %>% select(-ended)

# start_time <- Sys.time()
# other_raw <- get_usage_static(
#   conn,
#   from = report_from,
#   limit = Inf
# )
# end_time <- Sys.time()
# duration_get_other <- end_time - start_time

other_raw <- pin_get("katie/nonshiny_raw_usage", board = "rsconnect")
# other_raw <- read_rds(here::here("inst", "usage-report", "static_2021-06-14.rds"))

other <- other_raw %>% select(-variant_key, -rendering_id, -bundle_id) %>% 
  rename("started" = time)

# all_users <- get_users(conn, page_size = 500)


access_data <- rbind(shiny, other)
# readr::write_rds(data, file = here::here("inst","usage-report", "data.rds"))


access_details <- access_data %>% left_join(content_info, by = c(content_guid = "guid")) %>% 
  left_join(select(user_info, username, guid), by = c(user_guid = "guid"))

# WHAT IS NA for acl? 
# how is NA username accessing content that is acl, logged_in?
authenticated_access <- access_details %>% filter(access_type != "all") 
## ^ check this.

```

This content summary may contain privileged information. The report is generated
using the [RStudio Connect Server API](http://docs.rstudio.com/connect/api) and
the source code is [available online](https://github.com/sol-eng/connect-usage)
if you'd like to customize your analysis. Data is limited to the last `r
days_back` days.

The report uses the environment variables `CONNECT_SERVER` and `CONNECT_API_KEY`
to collect the data. To limit the results to a single publisher, use a publisher
API key.

Row 
-----------------------------------------------------------------------
What content is most popular?
```{r}

get_top_n_visited <- function(access_details, monthsback = months_back, n = Inf){
  access_details %>%
  filter(started > today() - dmonths(months_back)) %>% 
  mutate(month = round_date(started, "month")) %>% 
  group_by(month, content_guid, user_guid, name, title, owner_username, access_type, content_type, username) %>% 
  summarise(visits = n()) %>% 
  arrange(desc(visits)) %>% head(n)
}


summary_access <- get_top_n_visited(access_details, months_back)

## NEED HELP with this plot -- cant get it in pareto sort and want to filter results
ggplot(summary_access, aes(reorder(title, visits), visits)) + 
     geom_bar(stat = "identity") +  
     # coord_flip() + 
     labs(
       y = "Number of Visits",
       x = NULL
     ) + facet_wrap(~as.Date(month), scales = "free")


get_top_n_visitors <- function(access_details, monthsback = months_back, n = Inf){
  access_details %>%
    filter(!is.na(user_guid)) %>% 
  filter(started > today() - dmonths(months_back)) %>% 
  mutate(month = round_date(started, "month")) %>% 
  group_by(month, user_guid, name, title, owner_username, access_type, content_type, username) %>% 
  summarise(visits = n()) %>% arrange(desc(visits)) %>% head(n)
}


  

# Create top N chart of most frequently visited pieces of content. 
# Also create filter by publisher
# and summary of number of things published by usernae



```


```{r}


access_details %>% 
  filter(username == "katie") %>% group_by(content_guid, title, name, owner_username, content_type) %>% 
  summarise(visits = n()) %>% arrange(desc(visits)) 
#what content has a user visited?
get_user_access_activity <- function(access_details, user_guid) {
  access_details %>% filter(user_guid == !!user_guid)
}

get_user_access_activity(access_details, my_guid) %>% 
  get_top_n_visited()

#what users visit a piece of content most?
get_content_access_activity <- function(access_details, content_guid){
  access_details %>% filter(content_guid == !!content_guid)
}


get_content_access_activity(authenticated_access, (get_top_n_visited(authenticated_access)$content_guid)[3]) %>% 
  get_top_n_visitors()

#what apps have the largest number of users
authenticated_access %>% get_top_n_visitors()

```
 
